Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-14 doc/thesis/preamble.tex
Writing from last night
Started writing intro for BA methods section

\documentclass[11pt]{report}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage[top=1in, bottom=1in, inner=1.25in, outer=1in]{geometry}
\usepackage{setspace}
\usepackage[backend=biber, style=numeric-comp, sorting=none]{biblatex}
\usepackage{nicefrac}
\usepackage{amsmath, amssymb}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nonumberlist]{glossaries}
\usepackage{glossary-mcols}
\usepackage{cleveref}
\usepackage{array}
\usepackage{textcomp}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
\usepackage[titletoc]{appendix}
\usepackage{tocloft}
\usepackage[normalem]{ulem}
\usepackage{calc}

@@

\let\mref\cref
\let\Mref\Cref
\let\mtextcite\textcite
\let\mautocite\autocite
\renewcommand{\cref}[1]{\mbox{\mref{#1}}}
\renewcommand{\Cref}[1]{\mbox{\Mref{#1}}}
\renewcommand{\textcite}[1]{\mbox{\mtextcite{#1}}}
\renewcommand{\autocite}[1]{\mbox{\mautocite{#1}}}
\newcommand{\add}[1]{\color{blue}\uline{#1} \color{black}}
\newcommand{\madd}[1]{\color{blue}\underline{#1} \color{black}}
\newcommand{\del}[1]{\color{red}\sout{#1} \color{black}}
% http://tex.stackexchange.com/a/20612/60841
\newsavebox\CBox
\newcommand\mdel[1]{%
  \color{red}%
  \ifmmode\sbox\CBox{$#1$}\else\sbox\CBox{#1}\fi%
  \makebox[0pt][l]{\usebox\CBox}%
  \rule[0.5\ht\CBox-0.25pt]{\wd\CBox}{0.5pt}
  \color{black}%
}
%TC:macro \del [ignore]
%TC:macro \mdel [ignore]

\newcommand{\N}{\mathcal{N}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\L}{\mathcal{L}}

@@

\DeclareMathOperator{\Exponential}{Exponential}
\DeclareMathOperator{\Uniform}{Uniform}
\DeclareMathOperator{\DiscreteUniform}{DiscreteUniform}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\inc}{in}
\DeclareMathOperator{\out}{out}
\DeclareMathOperator{\ESS}{ESS}
\DeclareMathOperator{\nc}{nc}
\DeclareMathOperator{\nl}{nl}

\newacronym{MCMC}{MCMC}{Markov chain Monte Carlo}
\newacronym{ER}{ER}{Erd\H{o}s-R\'enyi}
\newacronym{BA}{BA}{Barab\'asi-Albert}
\newacronym{WS}{WS}{Watts-Strogatz}
\newacronym{SI}{SI}{susceptible-infected}
\newacronym{SVM}{SVM}{support vector machine}
\newacronym{SVR}{SVR}{support vector regression}
\newacronym{kSVM}{kSVM}{kernel support vector machine}
\newacronym{kSVR}{kSVR}{kernel support vector regression}
\newacronym{PCA}{PCA}{principal components analysis}
\newacronym{kPCA}{kPCA}{kernel principal components analysis}
\newacronym{SMC}{SMC}{sequential Monte Carlo}
\newacronym{ABC}{ABC}{approximate Bayesian computation}
\newacronym{nltt}{nLTT}{normalized lineages-through-time}
\newacronym{ltt}{LTT}{lineages-through-time}
\newacronym{pdf}{pdf}{probability density function}
\newacronym{rv}{rv}{random variable}
\newacronym{ML}{ML}{maximum likelihood}
\newacronym{MAP}{MAP}{maximum \textit{a posteriori}}
\newacronym{GSL}{GSL}{GNU scientific library}
\newacronym{SIR}{SIR}{susceptible-infected-recovered}
\newacronym{IS}{IS}{importance sampling}
\newacronym{SIS}{SIS}{sequential importance sampling}
\newacronym{HMM}{HMM}{hidden Markov model}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{HPD}{HPD}{highest posterior density}
\newacronym{HDI}{HDI}{highest density interval}
\newacronym{HIV}{HIV}{human immunodeficiency virus}
\newacronym{SARS}{SARS}{severe acute respiratory syndrome}
\newacronym{ODE}{ODE}{ordinary differential equation}
\newacronym{GLM}{GLM}{generalized linear model}
\newacronym{tasp}{TasP}{treatment as prevention}
\newacronym{MH}{MH}{Metropolis-Hastings}
\newacronym{GTR}{GTR}{generalized time-reversible}
\newacronym{ESS}{ESS}{expected sample size}
\newacronym{MSM}{MSM}{men who have sex with men}
\newacronym{ERGM}{ERGM}{exponential random graph model}
\newacronym{IDU}{IDU}{injection drug users}
\newacronym{ANOVA}{ANOVA}{analysis of variance}
\newacronym{MANOVA}{MANOVA}{multivariate analysis of variance}
\newacronym{AIC}{AIC}{Akaike information criterion}
\newacronym{POSIX}{POSIX}{Portable Operating System Interface}
\newacronym{IQR}{IQR}{interquartile range}
\newacronym{MPI}{MPI}{message passing interface}
\newacronym{PA}{PA}{preferential attachment}

\newglossaryentry{alpha}{
  name=\ensuremath{\alpha},
  description=preferential attachment power parameter in Barab\'asi-Albert networks
}
\newglossaryentry{m}{
  name=\ensuremath{m},
  description=number of edges added per vertex when constructing a Barab\'asi-Albert network
}
\newglossaryentry{N}{
  name=\ensuremath{N},
  description=total number of nodes in a contact network
}
\newglossaryentry{I}{
  name=\ensuremath{I},
  description=number of infected nodes in a contact network at the time of
  transmission tree sampling
}
\newglossaryentry{gamma}{
  name=$\gamma$,
  description=exponent of power-law degree distribution in scale-free networks
}
\newglossaryentry{p}{
  name=\ensuremath{p},
  description=edge density parameter in Erd\H{o}s-R\'enyi networks
}
\newglossaryentry{lambda}{
  name=\ensuremath{\lambda},
  description=decay factor meta-parameter for tree kernel
}
\newglossaryentry{sigma}{
  name=\ensuremath{\sigma},
  description=radial basis function variance meta-parameter for tree kernel
}
\newglossaryentry{n}{
  name=\ensuremath{n},
  description=number of particles used for sequential Monte Carlo
}
\newglossaryentry{M}{
  name=\ensuremath{M},
  description=number of simulated datasets per particle in ABC-SMC
}
\newglossaryentry{alphaess}{
  name=\ensuremath{\alpha_{\ESS}},
  description=per-iteration rate of expected sample size decay in adaptive ABC-SMC
}
\newglossaryentry{Theta}{
  name=\ensuremath{\Theta},
  description=parameter space for a given mathematical model
}

>>>>

\documentclass[11pt]{report}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage[top=1in, bottom=1in, inner=1.25in, outer=1in]{geometry}
\usepackage{setspace}
\usepackage[backend=biber, style=numeric-comp, sorting=none]{biblatex}
\usepackage{nicefrac}
\usepackage{amsmath, amssymb}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[hidelinks]{hyperref}
\usepackage[acronym,nonumberlist]{glossaries}
\usepackage{glossary-mcols}
\usepackage{cleveref}
\usepackage{array}
\usepackage{textcomp}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}
\usepackage[titletoc]{appendix}
\usepackage{tocloft}
\usepackage[normalem]{ulem}
\usepackage{calc}
\usepackage{twoopt}

@@

\let\mref\cref
\let\Mref\Cref
\let\mtextcite\textcite
\let\mautocite\autocite
\let\mciteauthor\citeauthor
\renewcommand{\cref}[1]{\mbox{\mref{#1}}}
\renewcommand{\Cref}[1]{\mbox{\Mref{#1}}}
\renewcommandtwoopt{\textcite}[3][][]{\mbox{\mtextcite[#1][#2]{#3}}}
\renewcommandtwoopt{\autocite}[3][][]{\mbox{\mautocite[#1][#2]{#3}}}
\renewcommand{\citeauthor}[1]{\mbox{\mciteauthor{#1}}}
\newcommand{\add}[1]{\color{blue}\uline{#1} \color{black}}
\newcommand{\madd}[1]{\color{blue}\underline{#1} \color{black}}
\newcommand{\del}[1]{\color{red}\sout{#1} \color{black}}
% http://tex.stackexchange.com/a/20612/60841
\newsavebox\CBox
\newcommand\mdel[1]{%
  \color{red}%
  \ifmmode\sbox\CBox{$#1$}\else\sbox\CBox{#1}\fi%
  \makebox[0pt][l]{\usebox\CBox}%
  \rule[0.5\ht\CBox-0.25pt]{\wd\CBox}{0.5pt}
  \color{black}%
}
%TC:macro \del [ignore]
%TC:macro \mdel [ignore]

\DeclareMathAlphabet{\mathcal}{OMS}{cmsy}{m}{n}
\newcommand{\N}{\mathcal{N}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\L}{\mathcal{L}}

@@

\DeclareMathOperator{\Exponential}{Exponential}
\DeclareMathOperator{\Uniform}{Uniform}
\DeclareMathOperator{\DiscreteUniform}{DiscreteUniform}
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\inc}{inc}
\DeclareMathOperator{\out}{out}
\DeclareMathOperator{\ESS}{ESS}
\DeclareMathOperator{\nc}{nc}
\DeclareMathOperator{\nl}{nl}

\newacronym{MCMC}{MCMC}{Markov chain Monte Carlo}
\newacronym{ER}{ER}{Erd\H{o}s-R\'enyi}
\newacronym{BA}{BA}{Barab\'asi-Albert}
\newacronym{WS}{WS}{Watts-Strogatz}
\newacronym{SI}{SI}{susceptible-infected}
\newacronym{SVM}{SVM}{support vector machine}
\newacronym{SVR}{SVR}{support vector regression}
\newacronym{kSVM}{kSVM}{kernel support vector machine}
\newacronym{kSVR}{kSVR}{kernel support vector regression}
\newacronym{PCA}{PCA}{principal components analysis}
\newacronym{kPCA}{kPCA}{kernel principal components analysis}
\newacronym{SMC}{SMC}{sequential Monte Carlo}
\newacronym{ABC}{ABC}{approximate Bayesian computation}
\newacronym{nltt}{nLTT}{normalized lineages-through-time}
\newacronym{ltt}{LTT}{lineages-through-time}
\newacronym{pdf}{pdf}{probability density function}
\newacronym{rv}{rv}{random variable}
\newacronym{ML}{ML}{maximum likelihood}
\newacronym{MAP}{MAP}{maximum \textit{a posteriori}}
\newacronym{GSL}{GSL}{GNU scientific library}
\newacronym{SIR}{SIR}{susceptible-infected-recovered}
\newacronym{IS}{IS}{importance sampling}
\newacronym{SIS}{SIS}{sequential importance sampling}
\newacronym{HMM}{HMM}{hidden Markov model}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{HPD}{HPD}{highest posterior density}
\newacronym{HDI}{HDI}{highest density interval}
\newacronym{HIV}{HIV}{human immunodeficiency virus}
\newacronym{SARS}{SARS}{severe acute respiratory syndrome}
\newacronym{ODE}{ODE}{ordinary differential equation}
\newacronym{GLM}{GLM}{generalized linear model}
\newacronym{tasp}{TasP}{treatment as prevention}
\newacronym{MH}{MH}{Metropolis-Hastings}
\newacronym{GTR}{GTR}{generalized time-reversible}
\newacronym{ESS}{ESS}{expected sample size}
\newacronym{MSM}{MSM}{men who have sex with men}
\newacronym{ERGM}{ERGM}{exponential random graph model}
\newacronym{IDU}{IDU}{injection drug users}
\newacronym{ANOVA}{ANOVA}{analysis of variance}
\newacronym{MANOVA}{MANOVA}{multivariate analysis of variance}
\newacronym{AIC}{AIC}{Akaike information criterion}
\newacronym{POSIX}{POSIX}{Portable Operating System Interface}
\newacronym{IQR}{IQR}{interquartile range}
\newacronym{MPI}{MPI}{message passing interface}
\newacronym{PA}{PA}{preferential attachment}
\newacronym{HCV}{HCV}{hepatitis C virus}

\newglossaryentry{alpha}{
  name=\ensuremath{\alpha},
  description=preferential attachment power parameter in Barab\'asi-Albert networks
}
\newglossaryentry{beta}{
  name=\ensuremath{\beta},
  description=transmission rate in susceptible-infected and susceptible-infected-removed epidemiological models
}
\newglossaryentry{nu}{
  name=\ensuremath{\nu},
  description=recovery rate in the susceptible-infected-removed epidemiological model
}
\newglossaryentry{m}{
  name=\ensuremath{m},
  description=number of edges added per vertex when constructing a Barab\'asi-Albert network
}
\newglossaryentry{N}{
  name=\ensuremath{N},
  description=total number of nodes in a contact network
}
\newglossaryentry{I}{
  name=\ensuremath{I},
  description=number of infected nodes in a contact network at the time of
  transmission tree sampling
}
\newglossaryentry{gI}{
  name=\ensuremath{\mathcal{I}},
  description=set of infected nodes in Gillespie simulation
}
\newglossaryentry{gR}{
  name=\ensuremath{\mathcal{R}},
  description=set of recovered nodes in Gillespie simulation
}
\newglossaryentry{gS}{
  name=\ensuremath{\mathcal{S}},
  description=set of recovered nodes in Gillespie simulation
}
\newglossaryentry{gD}{
  name=\ensuremath{\mathcal{D}},
  description=set of discordant edges in Gillespie simulation
}
\newglossaryentry{gamma}{
  name=\ensuremath{\gamma},
  description=exponent of power-law degree distribution in scale-free networks
}
\newglossaryentry{p}{
  name=\ensuremath{p},
  description=edge density parameter in Erd\H{o}s-R\'enyi networks
}
\newglossaryentry{lambda}{
  name=\ensuremath{\lambda},
  description=decay factor meta-parameter for tree kernel
}
\newglossaryentry{sigma}{
  name=\ensuremath{\sigma},
  description=radial basis function variance meta-parameter for tree kernel
}
\newglossaryentry{n}{
  name=\ensuremath{n},
  description=number of particles used for sequential Monte Carlo
}
\newglossaryentry{M}{
  name=\ensuremath{M},
  description=number of simulated datasets per particle in ABC-SMC
}
\newglossaryentry{alphaess}{
  name=\ensuremath{\alpha_{\ESS}},
  description=per-iteration rate of expected sample size decay in adaptive ABC-SMC
}
\newglossaryentry{Theta}{
  name=\ensuremath{\Theta},
  description=parameter space for a given mathematical model
}
\newglossaryentry{T}{
  name=\ensuremath{T},
  description=a transmission tree
}
\newglossaryentry{tmax}{
  name=\ensuremath{t_{\max}},
  description=user-defined cutoff time at which to stop Gillespie simulation
}
\newglossaryentry{t}{
  name=\ensuremath{t},
  description=time since initial infection of index case in an epidemic
}
\newglossaryentry{rho}{
  name=\ensuremath{\rho},
  description=distance function for approximate Bayesian computation
}
\newglossaryentry{epsilon}{
  name=\ensuremath{\varepsilon},
  description=distance function for approximate Bayesian computation
}
\newglossaryentry{q}{
  name=\ensuremath{q},
  description=proposal function for Metropolis-Hastings kernel
}
